---
title: "hmk_04"
author: "Bailey Morgan"
format: gfm
editor: visual
---

# Homework 4 ggplot

Note: I don't really think this is a good plot... but it's as good as *I* could get it. :/

```{r, message = FALSE}
library(tidyverse)

four.minutes <- read_csv("good_data?.csv")
```

I had to re-reorganize my data to make it R-friendly, and I only included one time point at 4 minutes beacuse I couldn't figure out a good way to do it over time.

## Attempt 1
```{r}
good.plot <- ggplot(four.minutes)+
  geom_point(aes(x = Test.Condition, y = TE))+
  geom_point(aes(x = Test.Condition, y = TE_IsoAMP), color = "blue")+
  geom_point(aes(x = Test.Condition, y = `0.5M.EDTA`), color = "red")+
  geom_point(aes(x = Test.Condition, y = `0.3M.EDTA`), color = "yellow")+
  geom_point(aes(x = Test.Condition, y = `160mM.EDTA`), color = "green")+
  scale_y_continuous(name = "Absorbance at 655 nm")
print(good.plot)
```

Normally, I represent my data in a bar graph, but using the scatterplot shows each data point, so outliers can be assesed without skewing the data by using an average or median. This plot was made by individually plotting the x and y variables to the geom and assigning them a color. However, this does not print the plot with a legend, so you have to look at the code to figure out whick color is what condition.

## Attempt 2
```{r}
better.plot <- ggplot(four.minutes, aes(x = Test.Condition)) +
  geom_point(aes(y = TE, color = "TE")) +
  geom_point(aes(y = TE_IsoAMP, color = "TE_IsoAMP")) +
  geom_point(aes(y = `0.5M.EDTA`, color = "0.5M.EDTA"))+
  geom_point(aes(y = `0.3M.EDTA`, color = "0.3M.EDTA"))+
  geom_point(aes(y = `160mM.EDTA`, color = "160mM.EDTA"))+
  scale_y_continuous(name = "Absorbance at 655 nm")+
  scale_x_discrete(name = "Test Condition")
print(better.plot)
```
After a bit of googling, I found that a little bit of rearranging produced the same plot, but with come changes to the colors as well as the addition of a legend.

When I daved this using `ggsave`, I made the height larger than the width so that the verticle axis would be longer so the points are a bit more spread out, because the default dimensions result in the points overlapping one another a bunch, which makes it more difficult to compare.

Again, I don't think that this is necessarily the best way to do this, and this plot is not acually that useful on its own for the pruposes I need it for, but I was not able to do anything more complicated at this time.